Supplementary Material

### 2024-12-02 manuscript/supplement.qmd
not on nsclc trials

```{r}
#| label: fig-consort-nsclc
#| fig-cap: "CONSORT diagram for non-small cell lung cancer (NSCLC) top candidate trials. Figure suggests four shortlisted candidates because both CheckMate017/057 have been both shortlisted and only differ in the squamous versus nonsquamous histological eligibility of the trial population."
#| out-width: "115%"

@@

>>>>

```{r}
#| label: fig-consort-nsclc
#| fig-cap: "CONSORT diagram for non-small cell lung cancer (NSCLC) top candidate trials."
#| out-width: "115%"

@@

*Note that @fig-consort-nsclc results in four shortlisted candidates because both CheckMate017/057 have been both shortlisted and only differ in the squamous versus nonsquamous histological eligibility of the trial population.*
